Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/2_method.tex
fix figure 1 and 2

\subsection{Skeleton-Based Graph Generation}
%\subsubsection{Node Generation}
\label{sec:skeletonization}
Most agglomeration methods create the region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
We here use the skeleton representation of the segmentation and reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
% a bit trivial, as everyone is doing this. maybe no need to mention
% \subsubsection{Node Pruning}
% %The simplest node generation strategy creates one node for every unique segment label in the input volume. 
% Some labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
% It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
% We prune these nodes from the graph by removing all segments with fewer than a empirical threshold $t_{seg} = 20,000$ voxels. 
% This removes on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}), leaving us with around $\TODO{XX}$ nodes per dataset (\TODO{X nodes per micrometer}). 
% Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.

>>>>

\subsection{Skeleton-Based Graph Generation}
%\subsubsection{Node Generation}
\label{sec:skeletonization}
Most region merging methods create the region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
We here use the skeleton representation of the segmentation and reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
% a bit trivial, as everyone is doing this. maybe no need to mention
% \subsubsection{Node Pruning}
% %The simplest node generation strategy creates one node for every unique segment label in the input volume. 
% Some labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
% It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
% We prune these nodes from the graph by removing all segments with fewer than a empirical threshold $t_{seg} = 20,000$ voxels. 
% This removes on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}), leaving us with around $\TODO{XX}$ nodes per dataset (\TODO{X nodes per micrometer}). 
% Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.
